Tracing the Stellar Halos of Massive Galaxies to 100 kpc at $0.3<z<0.5$ using Hyper Suprime-Cam

### 2017-06-06 draft/paper1_v11.tex
Jenny's comment: 3

%% ------------------------------------------------------------------------------------ %% 
	%Aforementioned results only use the 1-D \mden{} profiles that are baed on single 
	%band image and the flux-weighted isophotal shape, while more useful information 
	%can be gathered from the HSC images of these massive galaxies.
    So far, we have focused only on the 1-D \mden{} profiles from a single band.
	Here we turn to the ellipticity and $k$-corrected optical color profiles.
	We extract ellipticity profile using \texttt{Ellipse} by setting the shape of each 
	isophote free. 
	By applying the $i$-band isophotes to images of other bands in the 
	forced-photometry way \jenny{not sure what this means?}, we can also measure the color profiles too. 
	We apply Galactic extinction correction and \texttt{iSEDFit} $k$-correction to 
	both the $g-r$ and $g-i$ color profiles.
	The PSF smearing effect will make the central isophotal shape rounder than the 
	real value, while the seeing differences between filters will bias the central 
	color\footnote{Since the HSC $i$-band always has better seeing, the central color 
	will become redder when the seeing effect is not corrected.}. 
	At the same time, it is more difficult to extract reliable ellipticity and 
	color profiles out to 100 kpc: at low surface brightness region, isophotal shape 
	becomes unstable and easily affected by any contamination; the color profile in
	the outskirt also becomes very sensitive to background level and noise level in 
	either band. 
	In this work, we will focus on the median ellipticity and color profiles between 
	8--60 kpc where we can safely ignore the above issues.

>>>>

%% ------------------------------------------------------------------------------------ %% 
	%Aforementioned results only use the 1-D \mden{} profiles that are baed on single 
	%band image and the flux-weighted isophotal shape, while more useful information 
	%can be gathered from the HSC images of these massive galaxies.
    So far, we have focused only on the 1-D \mden{} profiles from a single band.
	Here we turn to the ellipticity and $k$-corrected optical color profiles.
	We extract ellipticity profile using \texttt{Ellipse} by setting the shape of each 
	isophote free. 
	We also apply the isophotal information derived in $i$-band directly to other 
	filters and extract 1-D $g-r$ and $g-i$ color profiles.
	Both Galactic extinction correction and \texttt{iSEDFit} $k$-correction are applied 
	to them.
	The PSF smearing effect will make the central isophotal shape rounder than the 
	real value, while the seeing differences between filters will bias the central 
	color\footnote{Since the HSC $i$-band always has better seeing, the central color 
	will become redder when the seeing effect is not corrected.}. 
	At the same time, it is more difficult to extract reliable ellipticity and 
	color profiles out to 100 kpc: at low surface brightness region, isophotal shape 
	becomes unstable and easily affected by any contamination; the color profile in
	the outskirt also becomes very sensitive to background level and noise level in 
	either band. 
	In this work, we will focus on the median ellipticity and color profiles between 
	8--60 kpc where we can safely ignore the above issues.
